A new machine-learning based prediction of survival in patients with end-stage liver disease

### 2022-08-09 analysis/article.Rmd
refactor: change title

---
# R markdown template taken from
# Dan Holmes <dtholmes@mail.ubc.ca>
# https://labrtorian.com/2019/08/26/rmarkdown-template-that-manages-academic-affiliations/
title: "A new model to predict survival in patients with end-stage liver disease"
subtitle: >
    Comparision against MELD, MELD-Na, MELD-Plus7.
abstract: >
  **Objectives**:
      The shortage of grafts for liver transplantation requires
      risk stratification and adequate allocation rules.
      This study aims to improve the model of end-stage liver disease (MELD)
      score for 90-day mortality prediction with the help of different
      machine-learning algorithms.

>>>>

---
# R markdown template taken from
# Dan Holmes <dtholmes@mail.ubc.ca>
# https://labrtorian.com/2019/08/26/rmarkdown-template-that-manages-academic-affiliations/
title: "A new machine-learning based prediction of survival in patients with end-stage liver disease"
subtitle: >
    Comparision against MELD, MELD-Na, MELD-Plus7.
abstract: >
  **Objectives**:
      The shortage of grafts for liver transplantation requires
      risk stratification and adequate allocation rules.
      This study aims to improve the model of end-stage liver disease (MELD)
      score for 90-day mortality prediction with the help of different
      machine-learning algorithms.
